SMT-Based Context-Bounded Model Checking for Embedded Systems (Position Paper)

### 2016-03-18 paper.tex
review BMC background

The basic idea behind BMC techniques is to check the violation of a given property at a given system's depth, {\it i.e.}, given a transition system \textit{M}, which is derived from the control-flow graph of the program; a property $\phi$ representing code correctness and/or system's behaviour; and a bound of iterations \textit{k}, which limits the loop unrolling, data structures, and context-switches in software, BMC thus unfolds the system \textit{k} times, in order to convert it into a verification condition $\psi$, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}.

SAT-based or SMT-based BMC procedures have been successfully applied to verify a large number of software systems, including single- and multi-threaded programs. In general, those BMC techniques were able to find subtle bugs in real embedded software systems, as reported in the literature~\cite{Clarke04,MerzFS12,CordeiroF11,Ivancic05,Cordeiro12}. However, the main criticism with respect to BMC techniques relies on completeness since they are able to prove system correctness only if an upper bound \textit{k} is known, {\it i.e.}, a bound that unfolds all loops and recursive functions to their maximum possible depth. Due to that limitation, BMC tools are typically susceptible to exhaustion of time or memory limits, when checking programs with loops whose bounds are too large or cannot be statically determined.

>>>>

The basic idea behind BMC techniques is to check the violation of a given property at a given system's depth, {\it i.e.}, given a transition system \textit{M}, which is derived from the control-flow graph of the program; a property $\phi$ representing program correctness and/or system's behaviour; and a bound of iterations \textit{k}, which limits the loop unrolling, data structures, and context-switches in software, BMC thus unfolds the system \textit{k} times, in order to convert it into a verification condition $\psi$, such that $\psi$ is \textit{satisfiable} if and only if $\phi$ has a counterexample of depth less than or equal to \textit{k}.

SAT-based or SMT-based BMC procedures have been successfully applied to verify a large number of hardware and software systems, including digital circuits, single- and multi-threaded programs. In general, those BMC techniques were able to find subtle bugs in real digital and embedded software systems, as reported in the literature~\cite{Clarke04,MerzFS12,CordeiroF11,Ivancic05,Cordeiro12}. However, the main criticism with respect to BMC techniques relies on completeness since they are able to prove system correctness only if an upper bound \textit{k} is known, {\it i.e.}, a bound that unfolds all loops and recursive functions to their maximum possible depth. Due to that limitation, BMC tools are typically susceptible to exhaustion of time or memory limits, when checking complex circuits implementation or programs with loops whose bounds are too large or cannot be statically determined.
